\begin{rSection}{Publications}

\textbf{Journal Articles}
\begin{description}[font=\normalfont]
\item[{[J3]}]{
    \textbf{Wuxi Li}, Yibo Lin, Meng Li, Shounak Dhar, David Z. Pan,
    ``UTPlaceF 2.0: A High-Performance Clock-Aware FPGA Placement Engine'',
    ACM Transactions on Design Automation of Electronic Systems (TODAES), 2017.
    (Submitted)
}

\item[{[J2]}]{
    \textbf{Wuxi Li}, Shounak Dhar, David Z. Pan,
    ``\href{http://ieeexplore.ieee.org/document/7984833/}{UTPlaceF: A Routability-Driven FPGA Placer with Physical and Congestion Aware Packing}'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2017.
    (Accepted)
}

\item[{[J1]}]{
    \textbf{Wuxi Li}, Hang Yuan, Wei Xu, Kunling Geng, Guoxing Wang,
    ``\href{http://ecst.ecsdl.org/content/52/1/1091.short}{An Optimization Procedure for Coil Design in a Dual Band Wireless Power and Data Transmission System}'',
    ECS Transactions (ECST), 2013.
}

\end{description}

\textbf{Conference Papers}
\begin{description}[font=\normalfont]
\item[{[C5]}]{
    Meng Li, Bei Yu, Yibo Lin, Xiaoqing Xu, \textbf{Wuxi Li}, David Z. Pan,
    ``A Practical Split Manufacturing Framework for Trojan Prevention via Simultaneous Wire Lifting and Cell Insertion'',
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), 2018.
}

\item[{[C4]}]{
    \textbf{Wuxi Li}, Meng Li, Jiajun Wang, David Z. Pan,
    ``UTPlaceF 3.0: A Parallelization Framework for Modern FPGA Global Placement'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2017.
    (\textbf{Invited Paper})
}

\item[{[C3]}]{
    Wei Ye, Yibo Lin, Xiaoqing Xu, \textbf{Wuxi Li}, Yiwei Fu, Yongsheng Sun, Canhui Zhan, David Z. Pan,
    ``\href{http://ieeexplore.ieee.org/document/8009178/}{Placement Mitigation Techniques for Power Grid Electromigration}'',
    IEEE International Symposium on Low Power Electronics and Design (ISLPED), 2017.
}

\item[{[C2]}]{
    \textbf{Wuxi Li}, Shounak Dhar, David Z. Pan,
    ``\href{http://ieeexplore.ieee.org/document/7827643/}{UTPlaceF: A Routability-Driven FPGA Placer with Physical and Congestion Aware Packing}'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2016.
    (\textbf{Invited Paper, 1st-Place Award of ISPD 2016 Contest})
}

\item[{[C1]}]{
    Wei Xu, Xiyan Li, \textbf{Wuxi Li}, Hang Yuan, Guoxing Wang,
    ``\href{http://ieeexplore.ieee.org/document/6865159/}{Live demonstration: An Optimization Software and a Design Case of a Novel Dual Band Wireless Power and Data Transmission System}'',
    IEEE International Symposium on Circuits and Systems (ISCAS), 2014.
}

\end{description}

\end{rSection}
