%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{tabularx}
\usepackage{amsmath}

\name{Wuxi Li} % Your name
\address{University of Texas at Austin \\ Austin, TX 78712} % Your address
\address{wuxi.li@utexas.edu} % Your phone number and email
%\address{(512)~$\cdot$~660~$\cdot$~2477 \\ wuxi.li@utexas.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}

Physical design automation for VLSI

\end{rSection}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas at Austin, TX} \hfill {\em Jan. 2016 - Present} \\ 
Ph.D. student, Department of Electrical and Computer Engineering \\
Advisor: David Z. Pan \\
GPA: 4.0/4.0

{\bf University of Texas at Austin, TX} \hfill {\em Aug. 2013 - Dec. 2015} \\ 
M.S., Department of Electrical and Computer Engineering \\
GPA: 4.0/4.0

{\bf Shanghai Jiao Tong University, Shanghai, China} \hfill {\em Sep. 2009 - Jul. 2013} \\ 
B.S., School of Microelectronics \\
GPA: 90.1/100.0

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Cadence Design System}{May 2016 - Dec. 2016}{Software Development Intern}{Austin, TX}
\item Fast buffer insertion
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Apple Inc.}{Sep. 2014 - Dec. 2015}{Physical Design Intern}{Cupertino, CA \& Austin, TX}
\item Low-power flip-flop design
\item Static timing analysis
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{ARM Inc.}{May. 2014 - Aug. 2014}{Memory Design Intern}{Austin, TX}
\item Fast memory leakage measurement
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{ECE Department, University of Texas at Austin}{Aug. 2013 - Present}{Graduate Student}{Austin, TX}
\item Research Assistant
\item Teaching Assistant of VLSI-II, Spring 2017
\item Teaching Assistant of VLSI-II, Spring 2016
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publication}

{\bf Journal Papers}
\begin{itemize}
    \item [{[J2]}] \textbf{Wuxi Li}, Shounak Dhar, and David Z. Pan, "UTPlaceF: A Routability-Driven FPGA Placer with Physical and Congestion Aware Packing", IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2017. (accepted)
	\item [{[J1]}] \textbf{Wuxi Li}, Hang Yuan, Wei Xu, Kunling Geng, Guoxing Wang, "An Optimization Procedure for Coil Design in a Dual Band Wireless Power and Data Transmission System", ECS Transactions (ECST), 2013.
\end{itemize}
\vspace{0.3in}
{\bf Conference Papers}
\begin{itemize}
    \item [{[C3]}] Wei Ye, Yibo Lin, Xiaoqing Xu, \textbf{Wuxi Li}, Yiwei Fu, Yongsheng Sun, Canhui Zhan and David Z. Pan, "Placement Mitigation Techniques for Power Grid Electromigration", IEEE International Symposium on Low Power Electronics and Design (ISLPED), Taipei, Jul. 24-26, 2017. 
	\item [{[C2]}] \textbf{Wuxi Li}, Shounak Dhah, and David Z. Pan, "UTPlaceF: A Routability-Driven FPGA Placer with Physical and Congestion Aware Packing", IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2016. (\textbf{Invited Paper, 1st-Place Winner of ISPD'16 Contest})
    \item [{[C1]}] Wei Xu, Xiyan Li, \textbf{Wuxi Li}, Hang Yuan, Guoxing Wang, "Live demonstration: An Optimization Software and a Design Case of a Novel Dual Band Wireless Power and Data Transmission System", IEEE International Symposium on Circuits and Systems (ISCAS), 2014.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	COURSES
%----------------------------------------------------------------------------------------

\begin{rSection}{Courses}

VLSI I                                           \hfill Prof. Michael Orshansky \\
Computer Architecture                            \hfill Prof. Aater Suleman \\
Optimization Issues in VLSI CAD                  \hfill Prof. David Pan \\
VLSI II                                          \hfill Prof. Jacob Abraham \\
Engineering Programming Languages                \hfill Prof. Craig Chase \\
Verification of Digital Systems                  \hfill Dr. Jay Bhadra \\
VLSI Physical Design Automation                  \hfill Prof. David Pan \\
Database Management                              \hfill Dr. Stan Gunn \\
High-Speed Computer Arithmetic                   \hfill Prof. Earl Swartzlander \\
Metadata Generation/Interface and mass Datasets  \hfill Prof. Unmil Karadkar \\
Optimization in Engineering Systems              \hfill Prof. Ross Baldick \\ 

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
{\bf Programming Languages} \\
C/C++, Perl, Python, Verilog

{\bf EDA Tools} \\
Cadence Virtuoso, Synopsys Design Compiler, Synopsys IC Compiler, Synopsys PrimeTime

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{HONORS AND AWARDS}

1st-Place Winner of Clock-Aware FPGA Placement Contest               \hfill ISPD \hspace{0.1\textwidth} 2017 \\
A. Richard Newton Young Student Fellow                               \hfill DAC  \hspace{0.1\textwidth} 2016 \\
1st-Place Winner of Routability-Driven FPGA Placement Contest        \hfill ISPD \hspace{0.1\textwidth} 2016 \\
Graduation with Honor, College Graduate Excellence Award of Shanghai \hfill SJTU \hspace{0.1\textwidth} 2013 \\
Excellent Bachelor Dissertation Award (Top 39/3900+)                 \hfill SJTU \hspace{0.1\textwidth} 2013 \\
Toshiba Electronics Scholarship                                      \hfill SJTU \hspace{0.1\textwidth} 2012 \\
Academic Excellence Scholarship                                      \hfill SJTU \hspace{0.1\textwidth} 2011 \\
Academic Excellence Scholarship                                      \hfill SJTU \hspace{0.1\textwidth} 2010 \\

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
